Leveraged Volume Sampling - Summary

### 2019-02-26 summary/paper-summary.tex
updated volume sampling introduction

            This resultant $w_{S}$ is unbiased, which in turn allows the averaging of multiple results to reduce the variance.
            However, there is no high probability guarantee of a $(1+\epsilon)L(w^\ast)$ bound on $L(w_{S})$ for this procedure
            (as shown in \hyperref[sec:no_mult_bound_vol]{the following section}).

>>>>

            This resultant $w_{S}$ is unbiased, which in turn allows the averaging of multiple results to reduce the variance.
            This procedure can also be implemented efficiently using the \textit{"Reverse Iterative Sampling"} and \textit{"Fast Regularized
            Volume Sampling"} {\color{blue}\href{https://arxiv.org/abs/1710.05110}{\underline{algorithms}}}\footnote{\label{reg_vol_samp}"Subsampling
            for Ridge Regression via Regularized Volume Sampling"}.
            However, there is no high probability guarantee of a $(1+\epsilon)L(w^\ast)$ bound on $L(w_{S})$ for this procedure
            (as shown in \hyperref[sec:no_mult_bound_vol]{the following section}).

        \subsection{Leveraged Volume Sampling}
